%!TEX program = lualatex
\documentclass[10pt,a4paper,sans,colorlinks]{moderncv}
\input{config.tex}
\title{C.V.}
\setLargeGeometry
\setParagraphReducedSpacing
\setItemizeUseHyphen
\setEnumItemNoSep
\begin{document}
\setHyperrefBlueLinks
\makecvtitle
\vspace{-2em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Highlights}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
    \item Computer Scientist Ph.D. with multiple postdoc experiences and research in Applied Machine Learning.
    \item \href{https://scholar.google.com/citations?user=1bEOmkUAAAAJ&hl=en}{Google Scholar} with 50+ published papers, 160+ citations, h-index 7.
    \item Awarded  as Principal Investigator in a \href{https://www.rnp.br/en/rnp-and-microsoft-challenge-artificial-intelligence}{Microsoft-funded project} (video classification).
    \item Experience in technology transfer to the industry by standards on \href{http://www.itu.int/en/ITU-T/studygroups/2022-2024/16}{ITU-T SG16} and \href{http://forumsbtvd.org.br}{TV Forum}.
    \item Contributed to research communities (ACM MM, ACM MMSys, ACM IMX, Springer MTAP, WebMedia)
    \item Co-supervised under- and post-graduate students.
    \item Experience in teaching  (module design, invited talks) and promoting students' \href{https://webmedia.org.br/2022/en/lf-award/}{research on social impact}.
    \item Skilled in C++, Python, ML Frameworks, research/academic/standards writing, and open source.
\end{itemize}

\footnotetext[1]{See certificates at \url{https://alanlivio.github.io/certificates}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cventry{2024--today}{Lecturer in Computer Science Researcher}{University of Reading}{}{}{
    \begin{itemize}
        \item Teach Undergrad and MSc modules.
    \end{itemize}
}
\cventry{2021--2023}{Postdoc Researcher (ML projects at \href{https://lasp-ucl.github.io}{LASP lab})}{University College London (UCL)}{}{}{
    \begin{itemize}
        \item Co-supervised undergrad and M.Sc. students.
        \item Contributed to ACM SIGMM events as a reviewer and workshop organizer.
        \item Worked on an EPSRC-funded project to improve 360-video streaming with profile-based methods.
    \end{itemize}
}
\cventry{2017--2021}{Postdoc Researcher (ML and multimedia projects at \href{http://telemidia.puc-rio.br/}{TeleMidia Lab})}{Pontifical Catholic University of Rio de Janeiro (PUC-Rio)}{}{}{
    \begin{itemize}
        \item Co-supervised undergrad and M.Sc. students.
        \item Contributed to SBC WebMedia as a reviewer and workshop organizer.
        \item Lecturer assistant on ML postgraduate module.
        \item Principal Investigator in a \href{https://www.rnp.br/en/rnp-and-microsoft-challenge-artificial-intelligence}{Microsoft-funded project} to detect inappropriate content in educational video repositories.
        \item Team Leader on SBTVD conformance test suite for \gingaSBTVD~(profile D) to be used by TV manufacturers.
        \item Worked on a \href{https://www.inf.puc-rio.br/blog/laboratorio/btg-pactual/}{BTG Bank-funded project} to detect financial transaction risk and anomaly detection.
        \item Worked on an \href{http://wrnp.rnp.br/sites/wrnp2017/files/02_wrnp2017_poster_gt-sap_design.pdf}{RNP-funded project} to design a blockchain-based system for academic certificates.
    \end{itemize}
}
\cventry{2013--2017}{Ph.D. Fellow (multimedia projects at \href{http://telemidia.puc-rio.br/}{TeleMidia Lab})}{Pontifical Catholic University of Rio de Janeiro (PUC-Rio)}{}{}{
    \begin{itemize}
        \item \href{https://doi.org/10.17771/PUCRio.acad.32313}{Thesis on multimedia scene descriptions} used as contributions to TV standards.
        \item Worked on PUC-Rio implementation of \gingaITU~funded by software licensing to TV manufacturers.
        \item Worked on the SBTVD conformance test suite for \gingaSBTVD~(profiles A/B/C) to be used by TV manufacturers.
    \end{itemize}
}
\cventry{2012--2013}{Research Engineer}{Dynavideo}{}{}{
    \begin{itemize}
        \item Worked on a \href{http://www.ebc.com.br/brasil-4d}{World Bank-funded project} (Brasil4D) to transmit interactive government TV content to low-income families. It received multiple awards from TV Associations.
    \end{itemize}
}
\cventry{2010--2012}{M.Sc. Fellow (multimedia projects at \href{https://lavid.ufpb.br/}{Lavid Lab})}{Federal University of Paraiba (UFPB)}{}{}{
    \begin{itemize}
        \item \href{https://dl.acm.org/doi/10.1145/2526188.2526239}{Thesis on  IBB TV app stores} used as contributions to TV standards.
        \item Lecturer and module design for Introduction to Programming (C language).
        \item Team leader on an RNP-funded project (\href{https://memoria-ctic.rnp.br/ctic/ginga-appstore.html}{GingaAppStore}) to design a broadband system to deliver TV apps.
    \end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cventry{2013--2017}{Ph.D. in Computer Science}{Pontifical Catholic University of Rio de Janeiro (PUC-Rio)}{}{}{}
\cventry{2010--2012}{M.Sc. in Computer Science}{Federal University of Paraiba (UFPB)}{}{}{}
\cventry{2005--2009}{BSc. in Computer Science}{}{}{}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Funding \& Awards}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cventry{2019}{\href{https://www.rnp.br/en/rnp-and-microsoft-challenge-artificial-intelligence}{Grant for video analysis} as Principal Investigator (funded 2 MSc students for 1 year)}{Microsoft}{}{}{}
\cventry{2019-2022}{Multiple Travels Awards}{ACM}{}{}{
    \begin{itemize}
        \item SIGMM Travel Award for MMSys (2022), SIGHI Gary Marsden Travel Award for IMX(2022), SIGWeb Travel Award for DocEng(2019).
    \end{itemize}
}
\cventry{2013-2014}{Brasil4D Awards}{TV Associations}{}{}{
    \begin{itemize}
        \item \href{https://programafrida.net/archivos/project/brasil-4d}{FRIDA Innovative TV} (2014), \href{http://set.org.br/artigos/ed137/137_revistadaset_70.pdf}{SET Conference best TV interactivity solution} for Brasil4D project (2013), \href{https://www.premiotv.com/es/ganadores-es/ganadores-2013-es}{PremioTV on Innovation and Creativity(2013)}
    \end{itemize}
}
\cventry{2012}{\href{https://memoria-ctic.rnp.br/ctic/ginga-appstore.html}{GingaAppStore} project: on User friendliness \href{https://itu.int/en/ITU-T/challenges/pages/iptv.aspx}{IPTV Application Challenge}}{ITU}{}{}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Publications}
\href{https://scholar.google.com/citations?user=1bEOmkUAAAAJ&hl=en}{Google Scholar} shows 50+ published papers, 160+ citations, h-index 7. See below recent and selected publications.
\newline\cventry{
    \href{https://www.sciencedirect.com/science/article/pii/B9780323917551000092}{2022}
}{Elsevier Book Chapter}{}{}{}{}
\cventry{\href{https://dl.acm.org/doi/10.1145/3524273.3528187}{2022}}{ACM Multimedia Systems}{}{}{}{}
\cventry{
    \href{https://link.springer.com/article/10.1007/s11042-016-3846-8}{2016},
    \href{https://link.springer.com/article/10.1007/s11042-020-09645-4}{2020}
}{Springer Journal on Multimedia Tools and Applications}{}{}{}{}
\cventry{
    \href{https://ieeexplore.ieee.org/abstract/document/9327927}{2020}
}{IEEE Symposium on Multimedia (ISM)}{}{}{}{}
\cventry{
    \href{https://dl.acm.org/doi/abs/10.1145/3428658.3430972}{2020},
    \href{https://dl.acm.org/doi/abs/10.1145/3428658.3430966}{2020},
    \href{https://dl.acm.org/doi/abs/10.1145/3428658.3430967}{2020},
    \href{https://dl.acm.org/doi/abs/10.1145/3470482.3479635}{2021},
    \href{https://dl.acm.org/doi/abs/10.1145/3470482.3479632}{2021},
    \href{https://dl.acm.org/doi/abs/10.1145/3470482.3479639}{2021}
}{SBC WebMedia}{}{}{}{}
\cventry{
    \href{https://dl.acm.org/doi/abs/10.1145/3342558.3345400}{2019}
}{ACM Symposium on Document Engineering}{}{}{}{}
\cventry{
    \href{https://ieeexplore.ieee.org/abstract/document/8901743}{2019}
}{IEEE Multimedia Signal Processing}{}{}{}{}

\subsection{Research Committees}

\cventry{2020-today}{Reviewer and chair}{ACM \href{http://www.sigmm.org/}{Special Interest Group on Multimedia}}{}{}{
    \begin{itemize}
        \item ACM MM: reviewer (2022, 2023), area chair (2022). 
        \item ACM MMSys: MMVE review (2021, 2022, 2023) and demo chair (2022).
        \item ACM IMX: reviewer (2022) and area chair (2022).
        \item ACM QoMex: reviewer (2023).
    \end{itemize}
}
\cventry{2019-today}{Reviewer and chair}{SBC \href{http://comissoes.sbc.org.br/ce-webmedia/comite.html}{WebMedia}}{}{}{
    \begin{itemize}
        \item WebMedia: Steering Committee (2018-2020), reviewer (2018-today), chair of Undergrad workshop (2018), chair of Demos workshop (2019-2022), and chair of Social Impact workshop (2019-2022).
    \end{itemize}
}
\cventry{2022-today}{Reviewer}{Springer}{}{}{
    \begin{itemize}
        \item Journal of Multimedia Tools and Applications (2022-today).
        \item Iberoamerican Conference on TV Applications and Usability (2021, 2023).
    \end{itemize}
}

\subsection{Industry Committees}

\cventry{2017-2021}{Academic member at \href{https://forumsbtvd.org.br/}{Technical Module} contributing to \gingaSBTVD}{Brazilian TV Forum (SBTVD).}{}{}{}

\cventry{2017-2021}{Academic member at \href{https://www.itu.int/en/ITU-T/studygroups/2017-2020/16/Pages/q13.aspx}{SG-16/Q13} contributing to \gingaITU}{International Telecommunication Union (ITU).}{}{}{}

\subsection{Training}
\cvline{University College London (UCL)}{Research Supervision, People Management Essentials, Fundamentals in Research Funding, GDPR, Data Protection.}
\cvline{Nature MasterClass}{Narrative Tools for Researchers, Focus on Peer Review.}{}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Teaching}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \cventry{2022-today}{Co-supervise undergrad and MSc projects.}{University College London (UCL)}{}{}{}
% \cventry{2018-2022}{Organizer of students workshop to promote research on social impact.}{SBC WebMedia}{}{}{}
% \cventry{2019}{Invited Lecturer on ML module to postgrad students (30+).}{Pontifical Catholic University of Rio de Janeiro (PUC-Rio)}{}{}{}
% \cventry{2018-2020}{Co-supervise undergrad and MSc projects.}{}{}{}{}
% \cventry{2013}{Lecturer on TV development to undergrad students (30+).}{}{}{}{}
% \cventry{2012}{Lecturer and module designer on TV development to South American countries professionals (30+)}{Japan International Cooperation Agency.}{}{}{}
% \cventry{2011}{Lecturer on Linux Administration to IT professionals (30+).}{RNP ESR}{}{}{}
% \cventry{2010}{Lecturer and course design on Programming Introduction (C language) to undergrad students (15+).}{Federal University of Paraiba (UFPB)}{}{}{}

% \subsection{Training}
% \cvline{University College London (UCL)}{Personal Tutoring, Diversity and Inclusion, Connected Learning Essentials}
% \cvline{LinkdinLearning}{Moodle 3.9.}


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Skills}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \cvline{Academic}{Execute a research agenda, scientific and standard writing.}
% \cvline{Teaching}{Course design, Moodle, and Connected Learning.}
% \cvline{Programming}{C++, Python, ML Frameworks, Java, JavaScript, Latex, GitHub, and CI/Docker.}{}{}{}
% \cvline{Social}{Growth mindset, teamwork, empathic communication, positive and make-it-happen attitudes.}
% \cvline{Languages}{English (fluent), Spanish (fluent), and Portuguese (mother tongue).}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
    \item Laura Toni, l.toni@ucl.ac.uk. Postdoc supervisor at UCL.
          %  Gower St, WC1E6BT, London, UK. Phone: 020 7679 2000
    \item Simone Barbosa, simone@inf.puc-rio.br. Ph.D. supervisor at PUC-Rio.
          %  Address: PUC-Rio, Marquês de São Vicente 225, CEP 22451-900, Rio de Janeiro, Brazil. Phone: +55 21 3527-1001
    \item Marcelo Moreno, moreno@ice.ufjf.br. ITU SG-16/Q13 and SBTVD collaborator.
          % Address: UFJF, Jose Lourenco Kelmer, CEP 36036-330, Juiz de Fora, Brazil.
    \item Roberto Azevedo, roberto.azevedo@disneyresearch.com. TeleMidia collaborator.
          % Address: Stampfenbachstrasse 48, 8006 Zürich, Switzerland.
\end{itemize}
% \item Sergio Colcher, colcher@inf.puc-rio.br. TeleMidia Lab head and PostDoc supervisor.
%  Address: PUC-Rio, Marquês de São Vicente 225, CEP 22451-900, Rio de Janeiro, Brazil.
% \item Guido Lemos, guido@lavid.ufpb.br. M.Sc. supervisor at UFPB.
% Address: UFPB, Mangabeira S/N, CEP 58033-455, João Pessoa, Brazil
% \item Guilherme Lima, guilherme.lima@ibm.com. A former researcher at TeleMidia lab.
% Address: IBM, Av. Pasteur 146, CEP 22290-240, Rio de Janeiro, Brazil.
% \item Carlos salles, csalles@deinf.ufma.br. Research partner.
% Address: UFMA, Av. dos Portugueses, 1966, CEP 65080-805, São Luis, Brazil.

\end{document}
