\documentclass[10pt,a4paper,sans,colorlinks]{moderncv}

% -- moderncv
% ----------------------------------------
\input{partials/config.tex}
\title{C.V.}
\hfGeometrySetLarge
\hfParagraphReduceSpacing
\hfEnumItemHyphen

% -- document
% ----------------------------------------

\begin{document}
\hfHyperrefSetupBlueLinks
\makecvtitle
\vspace{-2em}

\input{partials/short-intro.txt}

\section{Education}
\cventry{2017--2019}{PostDoc}{PUC-Rio}{Rio de Janeiro}{}{
  Title: Immersive MultiSensorial Video\newline
  Supervisors: Profa. Simone D.J. Barbosa and Prof. Sergio Colcher.
}
\cventry{2013--2017}{Ph.D. in Computer Science}{PUC-Rio}{Rio de Janeiro}{}{
  Title: {\href{https://doi.org/10.17771/PUCRio.acad.32313}{Extending multimedia languages to support multimodal user interactions}}\newline 
  Supervisors: Profa. Simone D.J. Barbosa and Prof. Luiz F.G. Soares~(\textit{in memoriam}).
  % \newline\cvitem{GPA}{8.5 out of 10}
}
\cventry{2010--2012}{M.Sc in Computer Science}{UFPB}{João Pessoa}{}{
  Title: \href{https://doi.org/10.17771/PUCRio.acad.32313}{A solution for running Ginga-NCL applications using second screen on Broad Band TV systems}\newline 
  Supervisor: Guido L.S. Filho.
  % \cvitem{GPA}{8.1 out of 10}
}
\cventry{2005--2009}{Bachelor in Computer Science}{UFPB}{João Pessoa}{}{
  % \cvitem{GPA}{7.7 out of 10}
}

\section{Skills}
\cvitem{Languages}{Portuguese (mothertongue), English (advanced), and Spanish (avarage)}
\cvitem{Research}{
  \begin{itemize}[mynosep]
    \item Research/stardard Writing (\href{https://scholar.google.com/citations?user=1bEOmkUAAAAJ&hl=en}{Google Scholar});
    \item Execute a research agenda and advise students.
    \item Participate in technical and standard committees;
  \end{itemize}
}
\cvitem{Social}{
  \begin{itemize}[mynosep]
    \item Good communication to work together in a team;
    \item Positive, make-it-happen, lead-by-example attitude;
    \item Collaborate with an international team.
  \end{itemize}
}
\cvitem{Software}{
  \begin{itemize}[mynosep]
    \item Maintain opensource software (\href{https://github.com/alanlivio}{Github});
    \item Languages: C++ (6yrs+), Lua, Java, HTML/JS, NCL, Python;
    \item Multimedia: Qt, Gstreamer, ffmpeg, Android/NDK;
    \item Web: nodejs, Flask, Jerkyll, Angular, AWS, Docker;
    \item Configuration: Linux, Bash, Git, Autotools, CMake, Latex;
    \item SW Process: Scrum, Kanban.
  \end{itemize}
}

\section{References}

\input{partials/people}

\section{Work Experience}
\cventry{2013--2021}{Research Engineer}{TeleMídia Lab, PUC-Rio}{Rio de Janeiro}{}{
  \textit{Skills: Research Writing, Machine Learning, Python, C++, Linux, Gstreamer, AWS, Scrum, Git, Autotools, NCL, Lua, and MPEG-2.}
  \begin{itemize}[mynosep]
    \item Worked on \href{https://www.rnp.br/en/rnp-and-microsoft-challenge-artificial-intelligence}{VideoMR  project} funded by RNP and Microsoft for detecting inappropriate content in video scenes;
    \item Worked on AML System (Anti Money Laundry) for BTG Bank, which uses Machine Learning to understand money transactions to identify money laundry;
    \item Worked on \href{{https://github.com/TeleMidia/ginga}}{Ginga reference implementation};
    \item Contributed Ginga/TV standards in Brazilian TV Forum (ABNT NBR 15606-2 series) and contributions in ITU SG-16/Q13 (H.761);
    \item Worked on \href{http://wrnp.rnp.br/sites/wrnp2017/files/02_wrnp2017_poster_gt-sap_design.pdf}{GT-RAP} project, which uses blockchain to enable document authentication and preservation of digital certificates.
  \end{itemize}
}

\cventry{2009--2013}{Research Engineer}{Lavid Lab, UFPB}{João Pessoa}{}{
  \textit{Skills: Research Writing, C++, Linux, Java, JNI, Scrum, Git, Autotools, NCL, Lua, and MPEG-2.}
  \begin{itemize}[mynosep]
    \item Worked on \href{http://www.ebc.com.br/brasil-4d}{Brasil4D" project "funded  by World Bank} to support the transmission of interactive video content (using Ginga technology) to 100 low-income families. Its results are published in a \href{http://documents.worldbank.org/curated/en/232621468230956108/pdf/809560WP0PORTU0Box0379824B00PUBLIC0.pdf}{public report};
    \item Worked on \href{http://www.redetic.rnp.br/ctic/2019/01/29/ginga-appstore/}{GingaAppStore project} to support broadband delivery interactive TV applications;
    \item Worked on \href{http://www.redetic.rnp.br/ctic/2019/01/29/arttvdi/}{Art TVDI project} for Agile Development and Reuse in DTV application;
    \item Worked on \href{http://www.redetic.rnp.br/ctic/2019/01/29/gingarap-gingafrevo/}{Ginga CDN project} to create reusable DTV middleware components.
  \end{itemize}
}

\cventry{2007--2008}{Software Developer}{\href{{https://www.dynavideo.com.br}}{Dynavideo}
}{João Pessoa}{}{
  \textit{Skills: C++, ARM, Linux, Java, JNI, Scrum, SVN, Autotools, NCL, Lua, and MPEG-2.}
  \begin{itemize}[mynosep]
    \item Worked on embedded systems division for digital TV products (MOPA) to implement TV receivers middleware.
  \end{itemize}
}

\section{Teaching Experience}
\cventry{2019}{Monitor. Multimedia and Machine Learning course.}{PUC-Rio}{Rio de Janeiro}{}{}
\cventry{2011}{Monitor. Linux administration course.}{ESR RNP}{Rio de Janeiro}{}{}
\cventry{2010}{Teaching internship. Introduction to Programming with C.}{UFPB}{João Pessoa}{}{}
\cventry{2018}{Monitor. Analysis and design of Algorithms.}{UFPB}{Rio de Janeiro}{}{}

\section{Selected Publications}
\begin{itemize}[mynosep]
  \item Alan L. V. Guedes, Roberto G. A. Azevedo, and Simone D.J. Barbosa. 2019. Extending Multimedia Languages to Support Multimodal User Interactions. \textit{Springer Multimedia Tools and Applications}.
  \item Pereira, Danne Makleyston G., Francisco José da S. e Silva, Carlos de Salles S. Neto, Davi Viana dos Santos, Luciano Reis Coutinho, and Alan L. V. Guedes. An Ontology-Based Approach to Integrate TV and IoT Middlewares. \textit{Springer Multimedia Tools and Applications}.
  \item Alan L. V. Guedes, Roberto G. A. Azevedo, Sérgio Colcher, and Simone D.J. Barbosa. Modeling Multimodal-Multiuser Interactions in Declarative Multimedia Languages. \textit{ACM Symposium on Document engineering (DocEng)}.
  \item Alan L. V. Guedes, Roberto G. A. Azevedo, Pascal Frossard, Sérgio Colcher, and Simone D.J. Barbosa. Subjective Evaluation of 360-degree Sensory Experiences. \textit{IEEE 21th International Workshop on Multimedia Signal Processing}.
\end{itemize}

To see other papers, including short and arXiv, please visit my \href{https://scholar.google.com/citations?user=1bEOmkUAAAAJ&hl=en}{Google Scholar}.
\end{document}

\section{Committees}
\cvitem{Brazilian conferences}{
  \begin{itemize}[mynosep]
    \item \href{http://www.webmedia.org.br}{WebMedia} (Brazilian Symposium on Multimedia and Web): Reviewer (2013-2019); Chair of Scientific Initiation Workshop (2018); Chair of Tools and Applications Initiation Workshop (2019); and Luiz Fernando Award Committee (2017-2019);
    \item CBIE (Brazilian Conference on Informatics for Education): Reviewer (2019);
    \item SBRT (Brazilian Conference of Telecommunications Society): Reviewer (2018).
  \end{itemize}
}
\cvitem{Brazilian TV Forum (SBTVD)}{
  \begin{itemize}[mynosep]
    \item  \href{https://forumsbtvd.org.br/}{Tecnical Module:} Contributor to \href{https://www.abntcolecao.com.br/normavw.aspx?
            ID=330432}{Ginga-NCL specification}.
  \end{itemize}
}
\cvitem{ITU}{
  \begin{itemize}[mynosep]
    \item \href{https://www.itu.int/en/ITU-T/studygroups/2017-2020/16/Pages/q13.aspx}{SG-16/Q13}: Contributor to
          \href{https://www.itu.int/rec/T-REC-H.761}{H.761/Ginga-NCL specification}.
  \end{itemize}
}
\cvitem{ACM}{
  \begin{itemize}[mynosep]
    \item IMX (TVX): Co-Reviewer (2015, 2019), Latim America Invited-Speaker (2020)
  \end{itemize}
}
\cvitem{IEEE}{
  \begin{itemize}[mynosep]
    \item QoMex: Co-Reviewer (2019)
    \item IEEE Multimedia: SeMP Workshop Reviewer (2019)
  \end{itemize}
}

\section{Awards}
\cvitem{Brasil 4D}{
  \begin{itemize}[mynosep]
    \item \href{http://set.org.br/artigos/ed137/137_revistadaset_70.pdf}{SET Conference 2013–Award "Best interactivity solution developed for digital terrestrial TV based on Ginga"}.
    \item \href{https://www.premiotv.com/es/ganadores-es/ganadores-2013-es}{OpenTV Awards} promoted by La Cumbre TV Abierta–Honorable mention in Innovation and Creativity
    \item \href{https://programafrida.net/archivos/project/brasil-4d}{FRIDA Awards} to innovative technological solutions with proven social impact in Latin America and the Caribbean.
  \end{itemize}
}
\cvitem{GingaStore}{
  \begin{itemize}[mynosep]
    \item \href{https://itu.int/en/ITU-T/challenges/pages/iptv.aspx}{ITU IPTV Application Challenge} Honorable mention in User friendliness Individual/SME for "Ginga Store" application.
  \end{itemize}
}

\section{Personal Interests}
\cvitem{Technology}{Open source and software with social impact (LF Award).}
\cvitem{Hobbies}{Nature, travelling, art, science-fiction, and fantasy literature.}